251 MA

### 2023-02-17 code/process.Rmd
write model code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
theme_set(theme_bw())
```

@@

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

@@

parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
  zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

@@

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         ratio_ss = replication_N/target_N,
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
        open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
        is_within=case_when(
            within_between=="within" ~ 1,
            within_between=="mixed" ~ 1,
            within_between=="between" ~ 0),
    log_trials=log(repeated_measure)) |> 
  select(target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, ratio_ss, change_platform, target_d_calc,
           stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
           predInt, p_orig, sub_rep)

@@

TODOs:
- will need to do selection of which things have complete cases for models
- will need to z-score things (in a recoverable way)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
theme_set(theme_bw())

model_location="code/models"
```

@@

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    #zval=beta/se
    #pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

@@

parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
 #zval=beta/se
    #pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

@@

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         log_ratio_ss = log(replication_N/target_N),
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
        open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
        is_within=case_when(
            within_between=="within" ~ 1,
            within_between=="mixed" ~ 1,
            within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
  predInt=as.numeric(predInt)) |> 
  select(target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
           stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
           predInt, p_orig, sub_rep)

@@

## z-score

z_data <- d_for_model |> 
  mutate(across(c("pub_year","log_p", "log_sample", "log_ratio_ss","target_d_calc", "log_trials"), ~scale(.)[,1], .names="z_{.col}"))

back_convert <- d_for_model |> 
  summarize(across(c("pub_year","log_p", "log_sample", "log_ratio_ss","target_d_calc", "log_trials"), ~mean(., na.rm=T), .names="mean_{.col}"),
         across(c("pub_year","log_p", "log_sample", "log_ratio_ss","target_d_calc", "log_trials"), ~sd(.,na.rm=T), .names="sd_{.col}"))

## check z-score

```{r}
# z_data |>
#   mutate(check_pub=pub_year - z_pub_year*back_convert$sd_pub_year+back_convert$mean_pub_year) |> 
#   filter(check_pub > .00001)
```

## tier 1 data
```{r}
data_tier1 <- z_data |> select(academic_year, sub_rep, 
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))

## tier 2 data
```{r}
data_tier2 <- z_data |> select(academic_year, sub_rep, 
                               p_orig, predInt,
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.))) 
```

## tier 3 data
```{r}
data_tier3 <- z_data |> select(academic_year, sub_rep, 
                               p_orig, predInt,
                               z_target_d_calc, z_log_p, 
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.))) 
```

# Models

priors <- c(set_prior("horseshoe(3)", class="b"),
            set_prior("normal(0,.5)", class="sd"),
            set_prior("lkj(1)", class="cor"))
```

```{r}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="bernoulli",
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        iter=100,
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r, eval=F}
tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="bernoulli",
                        data=data_tier2,
                        file=here(model_location, "tier2_predint"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r, eval=F}
tier2_porig <- brm(porig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        data=data_tier2,
                        file=here(model_location, "tier2_porig"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r, eval=F}
tier3_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                           z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="bernoulli",
                        data=data_tier3,
                        file=here(model_location, "tier3_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r, eval=F}
tier3_predint <- brm(predint ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                           z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="bernoulli",
                        data=data_tier3,
                        file=here(model_location, "tier3_predint"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

```{r, eval=F}
tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                           z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="bernoulli",
                        data=data_tier3,
                        file=here(model_location, "tier3_porig"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```
